Hardware-Accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-06-23 paper.tex
Sorted Boolean XOR method before Depth-Masking in Desktop performance chart (ref #19)
Updated results in desktop performance chart (ref #19)
Updated title of desktop performance chart (ref #19)
Updated caption of desktop performance chart (ref #19)

\begin{figure}
\centering
\begin{tikzpicture}
\begin{axis}[
    title=3.0 GHz P4 with NVIDIA GeForce 8500 GT,
    xlabel=Samples,
    ylabel=Frames Per Second]
\addplot coordinates {
  (100, 10)
  (200, 6)
  (300, 4)
  (400, 3)
  (500, 2)
};
\addlegendentry{Depth-masking}
\addplot coordinates {
  (100, 13)
  (200, 7)
  (300, 5)
  (400, 4)
  (500, 3)
};
\addlegendentry{Boolean XOR}
\addplot coordinates {
  (100, 18)
  (200, 9)
  (300, 6)
  (400, 5)
  (500, 4)
};
\addlegendentry{Slicing (uniforms)}
\addplot coordinates {
  (100, 15)
  (200, 8)
  (300, 5)
  (400, 4)
  (500, 3)
};
\addlegendentry{Slicing (attributes)}
\end{axis}
\end{tikzpicture}
\caption{
Chart showing performance measurements as number of samples varies.  Here the
slicing with uniforms method is fastest, followed by the slicing with attributes
method, and the Boolean XOR method.  The depth-masking method is slowest.
}
\label{desktop-performance-chart}
\end{figure}

>>>>

\begin{figure}
\centering
\begin{tikzpicture}
\begin{axis}[
    title=3.0 GHz Intel Pentium 4 with NVIDIA GeForce 8500 GT,
    xlabel=Samples,
    ylabel=Frames Per Second]
\addplot coordinates {
  (100, 4)
  (200, 3)
  (300, 2)
  (400, 1)
  (500, 1)
};
\addlegendentry{Boolean XOR}
\addplot coordinates {
  (100, 4)
  (200, 2)
  (300, 2)
  (400, 1)
  (500, 1)
};
\addlegendentry{Depth-masking}
\addplot coordinates {
  (100, 3)
  (200, 1)
  (300, 1)
  (400, 1)
  (500, 1)
};
\addlegendentry{Slicing (uniforms)}
\addplot coordinates {
  (100, 3)
  (200, 1)
  (300, 1)
  (400, 1)
  (500, 1)
};
\addlegendentry{Slicing (attributes)}
\end{axis}
\end{tikzpicture}
\caption{
Chart showing performance measurements as number of samples varies on an Intel
Pentium 4 system with an NVIDIA GeForce 8500 GT video card.
}
\label{desktop-performance-chart}
\end{figure}
